\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-08-30 NAR_DRAFT.tex
fix simulate

\subsection{Tumor simulations.}
We simulated realistic variant sites and allele frequencies using a branching process to simulate neutral evolution with no death.
Tumors were simulated with three different mutation profiles derived from combinations of COSMIC mutation signatures (\bkmcomment{website or citation}).
Each simulate profile includes a contribution from COSMIC mutation signature 1 which is found in nearly all tumors and is associated with spontaneous cytosine deamination.
The "Concentrated" profile is simulated with $\mathbf{\pi}$ set to an equal combination of the COSMIC signatures 1, 7, and 11, which has a large percentage of C $>$ T substitutions such as are often seen in cancers caused by UV exposure.
The "Intermediate" profile is simulated with $\mathbf{\pi}$ set to an equal combination of the COSMIC signatures 1, 4, and 5, which has been associated with tobacco carcinogens and is representative of some lung cancers.
The "Diffuse" profile is simulated with $\mathbf{\pi}$ set to an equal combination of the COSMIC signatures 1, 3, and 5, which has been associated with inactivating germline mutations in the BRCA1/2 genes leading to a deficiency in DNA double strand break repair.
The simulated mutation rate was $\mu = 3\cdot10^{-6}$.
Variants were selected from a combination of the Cancer Genome Atlas (TCGA) and Pan-cancer Analysis of Whole Genomes (PCAWG) databases, which include mutations found in all types of cancer.
Whole genome (100X depth), and whole exome (500X depth) reads were simulated from the GRCH38 reference genome using VarSim \cite{Mu2015}, and aligned with BWA \cite{Li2009a}, both with default parameters.
Variants were spiked to create tumors with Bamsurgeon with default parameters \cite{Ewing2015a},
and called with MuTect 1.1.7 \cite{Cibulskis2013} with the following parameters:

>>>>

\subsection{Tumor simulations.}
We simulated realistic variant sites and allele frequencies using a branching process to simulate neutral evolution with no death.
Tumors were simulated with three different mutation profiles derived from combinations of COSMIC mutation signatures (\bkmcomment{website or citation}).
Each simulated profile includes a contribution from COSMIC mutation signature 1 which is found in nearly all tumors and is associated with spontaneous cytosine deamination.
The "Concentrated" profile is simulated with $\mathbf{\pi}$ set to an equal combination of the COSMIC signatures 1, 7, and 11, which has a large percentage of C $>$ T substitutions such as are often seen in cancers caused by UV exposure.
The "Intermediate" profile is simulated with $\mathbf{\pi}$ set to an equal combination of the COSMIC signatures 1, 4, and 5, which has been associated with tobacco carcinogens and is representative of some lung cancers.
The "Diffuse" profile is simulated with $\mathbf{\pi}$ set to an equal combination of the COSMIC signatures 1, 3, and 5, which has been associated with inactivating germline mutations in the BRCA1/2 genes leading to a deficiency in DNA double strand break repair.
The simulated mutation rate was $\mu = 3\cdot10^{-6}$.
Variants were selected from a combination of the Cancer Genome Atlas (TCGA) and Pan-cancer Analysis of Whole Genomes (PCAWG) databases, which include mutations found in all types of cancer.
Whole genome (100X depth), and whole exome (500X depth) reads were simulated from the GRCH38 reference genome using VarSim \cite{Mu2015}, and aligned with BWA \cite{Li2009a}, both with default parameters.
Variants were spiked to create tumors with Bamsurgeon with default parameters \cite{Ewing2015a},
and called with MuTect 1.1.7 \cite{Cibulskis2013} with the following parameters:
